The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/accuracy.tex
Updated references to figures.

The first and most obvious way of judging accuracy is by visual inspection.
Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
\ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively.

@@

Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
skew-normal and normal approximations as a function of $p$ and $n$,
respectively. Again, the skew-normal outperforms the normal considerably in the
extreme ranges, with the two approximations converging as $n \rightarrow
\infty$ or $p \rightarrow 0.5$.

>>>>

The first and most obvious way of judging accuracy is by visual inspection.
Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
\ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
normal, and skew-normal at small values of $p$ for $n=25$, $n=50$, and $n=100$,
respectively.

@@

Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
\ref{app:figures} shows the MABS of the skew-normal and normal approximations
as a function of $p$ and $n$, respectively. Again, the skew-normal outperforms
the normal considerably in the extreme ranges, with the two approximations
converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.

### 2011-01-22 project/paper/method-of-moments.tex
Updated references to figures.

Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
estimate $\lambda$ as a function of $p$.\footnotemark As we would expect, it is
larger when $p$ is small and rapidly goes to 0 as $p$ approaches 0.5; for
example, when $p = 0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need
only be $\geq 3$, a trivial requirement to meet.

@@

Figure \ref{fig:sn-restriction-p-range} in appendix \ref{app:graphs} shows this
range as a function of $n$, this interval grows quickly as $n$ increases, and
for sufficiently large $n$, it becomes almost $(0, 1)$. For example, when
$n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is (0.00199,
0.99801).

>>>>

Figure \ref{fig:sn-restriction-least-n} in appendix \ref{app:figures} shows the
least sample size required to estimate $\lambda$ as a function of
$p$.\footnotemark As we would expect, it is larger when $p$ is small and
rapidly goes to 0 as $p$ approaches 0.5; for example, when $p = 0.01$, $n$ must
be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a trivial
requirement to meet.

@@

Figure \ref{fig:sn-restriction-p-range} in appendix \ref{app:figures} shows
this range as a function of $n$, this interval grows quickly as $n$ increases,
and for sufficiently large $n$, it becomes almost $(0, 1)$. For example, when
$n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is (0.00199,
0.99801).

### 2011-01-22 project/paper/output.tex
Updated references to figures.

Table \ref{tab:sn-approx-table} shows estimations of $SN(\mu, \sigma, \lambda)$
for common binomial distributions.

For those with an unusual combination of $n$ and $p$ not in the table, Appendix
\ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
parameters by hand.

@@

%\begin{figure}
%  \centering
%  \subfloat{\label{fig:mabs-n25}\includegraphics[width=0.8\textwidth]{../images/mabs-n25.png}}                
%  \\ \vspace{5mm}
%  \subfloat{\label{fig:mabs-n100}\includegraphics[width=0.8\textwidth]{../images/mabs-n100.png}}
%  \caption{MABS as a function of p}
%  \label{fig:mabs-fixed-n}
%\end{figure}
%
%\begin{figure}
%  \centering
%  \subfloat{\label{fig:mabs-p0.05}\includegraphics[width=0.8\textwidth]{../images/mabs-p005.png}}                
%  \\ \vspace{5mm}
%  \subfloat{\label{fig:mabs-p0.1}\includegraphics[width=0.8\textwidth]{../images/mabs-p01.png}}
%  \caption{MABS as a function of n}
%  \label{fig:mabs-fixed-p}
%\end{figure}

>>>>

Table \ref{tab:sn-approx-table} in appendix \ref{app:figures} shows estimations
of $SN(\mu, \sigma, \lambda)$ for common binomial distributions.

For those with an unusual combination of $n$ and $p$ not in the table, appendix
\ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
parameters by hand.

@@
